---
title: "Sex x Parental Edu Effect on Externalizing Symptoms n1051"
output: html_document
---

Uses ROIs from JNeurosci 2013 paper. Subset created using exclusion criteria from new n1601 data freeze


```{r include=FALSE}
library(ggplot2)
library(reshape2)
require(utils)
library(scales)
source("/home/sshanmugan/scripts/summarySE.R")
```


```{r include=FALSE}
data <- read.csv("/data/jux/BBL/projects/exec_extern_sex/inputData/data_agg/nback_n1051_from1601_jneurosciROIs_20180831.csv") #after 4 level exclusion, subsetted for complete data for extern, medu, fedu
data$sex01 <- as.factor(data$sex01)
```







list2x <- grep("nback_func", names(data), value = TRUE) #27 RO

namelist <- c(list2x)
list1a <- c("ace_group", "TD_status")
list1b <- c("lmp", "e2_pgml", "age", "meanRELrms","acexTD")
list3 <- c(list1a, list1b)

#part 3: run regression on each connectivity column
full.model.results_vif<-data.frame(matrix(NA,nrow=length(list3),ncol=length(namelist)))
colnames(full.model.results_vif)<- namelist
rownames(full.model.results_vif)<- list3

full.model.results_coeff<-data.frame(matrix(NA,nrow=length(list3),ncol=length(namelist)))
colnames(full.model.results_coeff)<- namelist
rownames(full.model.results_coeff)<- list3

full.model.results<-data.frame(matrix(NA,nrow=length(list3),ncol=length(namelist)))
colnames(full.model.results)<- namelist
rownames(full.model.results)<- list3



for (i in 1:length(namelist)){
  yvar <- namelist[i]
  newdata <- subset(data3, select=c("pid", "ace_group", "TD_status", yvar, "lmp", "e2_pgml", "age", "nback_meanRELrms", "total_overall"))
  newdata["yvar"] <- (newdata[,4])
  newdata <- subset(newdata, yvar != "NA")
  
  # xweight <- newdata1$months_no_hormones_121
  # yweight <- predict(full.model, newdata1, list(wt = xweight),type="response", level=0)
  # df <- as.data.frame(cbind(xweight, yweight))
  pl <- ggplot(newdata, aes(x=nback_meanRELrms, y=yvar, ymax=max(yvar)*1.05)) +  
    geom_point( stat="identity") +
    stat_smooth(method = "lm") + 
    ylab(paste(namelist[i])) + 
    xlab(paste("meanRELrms"))
  print(pl)
  
  
  
  try(full.model <- lme(yvar ~ ace_group + TD_status + ace_group*TD_status + lmp + e2_pgml + age + nback_meanRELrms + total_overall, random=list(pid=~1),  data=newdata))
  vif.lm <- vif.lme(full.model)
  vif.lm
  a <- vif.lm["ace_group1"]
  b <- vif.lm["TD_status1"]
  c <- vif.lm["lmp"]
  d <- vif.lm["e2_pgml"]
  e <- vif.lm["age"]
  f <- vif.lm["nback_meanRELrms"]
  g <- vif.lm["ace_group1:TD_status"]
  
  
  full.model.results_vif[1, i] <- a 
  full.model.results_vif[2, i] <- b
  full.model.results_vif[3, i] <- c
  full.model.results_vif[4, i] <- d
  full.model.results_vif[5, i] <- e
  full.model.results_vif[6, i] <- f
  full.model.results_vif[7, i] <- g
  
  
  #coefficients
  a <- summary(full.model)$tTable[2,1]
  b <- summary(full.model)$tTable[3,1]
  c <- summary(full.model)$tTable[4,1]
  d <- summary(full.model)$tTable[5,1]
  e <- summary(full.model)$tTable[6,1]
  f <- summary(full.model)$tTable[7,1]
  g <- summary(full.model)$tTable[9,1]
  
  
  full.model.results_coeff[1, i] <- a 
  full.model.results_coeff[2, i] <- b 
  full.model.results_coeff[3, i] <- c
  full.model.results_coeff[4, i] <- d
  full.model.results_coeff[5, i] <- e
  full.model.results_coeff[6, i] <- f
  full.model.results_coeff[8, i] <- g
  
  
  
  #pvalue
  a <- summary(full.model)$tTable[2,5]
  b <- summary(full.model)$tTable[3,5]
  c <- summary(full.model)$tTable[4,5]
  d <- summary(full.model)$tTable[5,5]
  e <- summary(full.model)$tTable[6,5]
  f <- summary(full.model)$tTable[7,5]
  g <- summary(full.model)$tTable[9,5]
  
  full.model.results[1, i] <- a 
  full.model.results[2, i] <- b 
  full.model.results[3, i] <- c
  full.model.results[4, i] <- d
  full.model.results[5, i] <- e
  full.model.results[6, i] <- f
  full.model.results[8, i] <- g
  
  lsmeans_data<-lsmeans(full.model, ~ ace_group+ TD_status + lmp + e2_pgml + age + nback_meanRELrms, random=list(pid=~1))
  sdata <- summary(lsmeans_data)
  #ace bargraphs
  pl <- ggplot(sdata, aes(x=ace_group, y=lsmean, fill=TD_status)) +
    geom_bar(position=position_dodge(), stat="identity", size=0.8, colour="black" ) +
    geom_errorbar(aes(ymin=lsmean-SE, ymax=lsmean+SE), width=.2, size=0.8, position=position_dodge(.9)) +
    scale_fill_manual(values=c("white", "grey40")) +
    ylab(paste(namelist[i])) +
    xlab(paste("ace_group")) +
    theme(legend.position="none") +
    scale_x_discrete(labels=c("Low ACE", "High ACE")) #+
  #scale_y_continuous(limits = c(0.3, 0.5), oob=rescale_none) 
  print(pl)
  
}





```{r include=FALSE}
yvar="externalizing_4factorv2"
data1 <- subset(data, select=c("scanid", yvar, "ageInYears", "sex01", "medu1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
data1<- subset(data1, medu1 != "NA") #n=1138
```

#No sex x maternal education interaction on externalizing symptoms, medu -> fewer symptoms 
Using bifactor scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ sex01*medu1 + sex01 + medu1 + ageInYears, data=data1)
summary(full.model)

full.model <- lm(yvar ~  sex01 + medu1 + ageInYears, data=data1)
summary(full.model)

ggplot(data1, aes(x=medu1, y=yvar, fill=sex01, color=sex01)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm")
```

#No interaction between age x sex x medu on externalizing symptoms
Using bifactor scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01*medu1 +medu1, data=data1)
summary(full.model)

#full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01 +medu1 + medu1*sex01, data=data1)
#summary(full.model)
```



```{r include=FALSE}
yvar="externalizing_4factorv2"
data1 <- subset(data, select=c("scanid", yvar, "ageInYears", "sex01", "fedu1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
data1<- subset(data1, fedu1 != "NA") #n=1058
```

#Sex x paternal education interaction on externalizing symptoms 
Using bifactor scores. Paternal education impact on male (more edu -> fewer externalizing symptoms), but not female.
```{r echo=FALSE}
full.model <- lm(yvar ~ sex01*fedu1 + sex01 + fedu1 + ageInYears, data=data1)
summary(full.model)

ggplot(data1, aes(x=fedu1, y=yvar, fill=sex01, color=sex01)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm") 
```

```{r echo=FALSE}
#full.model <- lm(yvar ~  sex01 + fedu1 + ageInYears, data=data1)
#summary(full.model)
```

#No interaction between age x sex x fedu on externalizing symptoms
Using bifactor scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01*fedu1 +fedu1, data=data1)
summary(full.model)

full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01 + fedu1*sex01 + fedu1, data=data1)
summary(full.model)

full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01 +fedu1, data=data1)
summary(full.model)
```
