---
title: "Sex Differences in Externalizing symptoms and d'"
output:
  html_document: default
  pdf_document: default
---

```{r include=FALSE}
library(ggplot2)
library(reshape2)
require(utils)
library(scales)
source("/home/sshanmugan/scripts/summarySE.R")
```


```{r include=FALSE}
data <- read.csv("/data/jux/BBL/projects/exec_extern_sex/inputData/data_agg/nback_n1154_from1601_20180827.csv")
data$sex1m1 <- ifelse(data$sex==1, 1,-1)
data$sex1m1 <- as.factor(data$sex1m1)
```

Histogram of age by sex

```{r, echo=FALSE, message=FALSE}
ggplot(data,aes(x=ageInYears, fill=sex1m1)) + geom_histogram()+facet_grid(~sex1m1)
```

```{r include=FALSE}

yvar="externalizing_4factorv2"
data1 <- subset(data, select=c("scanid", yvar, "ageInYears", "sex1m1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
```

#Sex differences in externalizing symptoms 
Using bifactor scores. One subject is missing symptom data. n=1153
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1, data=data1)
summary(full.model)
```

bar graph of age residualized externalizing by sex
```{r echo=FALSE}
resid1<- as.data.frame(residuals(full.model, type="pearson"))
names(resid1) <- "resid"
newdata1 <- cbind(data1, resid1)
newdata2<-subset(newdata1, select=c("scanid", "sex1m1", "yvar"))
mdata <- melt(newdata1, id=c("scanid", "sex1m1"))
sdata<- summarySE(mdata, measurevar="value", groupvars="sex1m1")
ggplot(sdata, aes(x=sex1m1, y=value, fill=sex1m1)) + 
  geom_bar(position=position_dodge(), stat="identity", size = 0.8, width=0.65) +
  geom_errorbar(aes(ymin=value-se, ymax=value+se), position=position_dodge(0.65), width=0.15, size=0.8)
```

Histogram of externalizing symptoms (bifactor)

```{r, echo=FALSE, message=FALSE}
ggplot(data1,aes(x=yvar, fill=sex1m1)) + geom_histogram(position="dodge")
```

```{r include=FALSE}
#full.model <- lm(externalizing_4factorv2 ~ ageInYears + sex1m1 + overall_psychopathology_4factorv2, data=data1)
#summary(full.model)
```

#Interaction between age and sex on externalizing symptoms
Using bifactor scores. One subject is missing symptom data. n=1153
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1 + ageInYears*sex1m1, data=data1)
summary(full.model)

ggplot(data1, aes(x=ageInYears, y=yvar, fill=sex1m1, color=sex1m1)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm") 
```


##########################
```{r include=FALSE}

yvar="externalizing_corrtraitsv2"
data1 <- subset(data, select=c("scanid", yvar, "ageInYears", "sex1m1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
```

#Sex differences in externalizing symptoms 
Using correlated trait scores. One subject is missing symptom data. n=1153
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1, data=data1)
summary(full.model)
```

#Interaction between age and sex on externalizing symptoms
Using correlated trait scores. One subject is missing symptom data. n=1153
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1 + ageInYears*sex1m1, data=data1)
summary(full.model)

ggplot(data1, aes(x=ageInYears, y=yvar, fill=sex1m1, color=sex1m1)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm") 
```

#############

```{r include=FALSE}
yvar="nbackBehAllDprime"
data1 <- subset(data, select=c("scanid", yvar, "ageInYears", "sex1m1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
```

#Sex differences in overall d'
n=1154
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1, data=data1)
summary(full.model)
```

#Interaction between age and sex on overall d'
n=1154
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1 + ageInYears*sex1m1, data=data1)
summary(full.model)

ggplot(data1, aes(x=ageInYears, y=yvar, fill=sex1m1, color=sex1m1)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm") 
```













########################################
#Only subjects with ADD, ODD, CON = 4, n=447
```{r include=FALSE}
#subset to only subjects with ADD, ODD, Con = 4
dataa<- subset(data, goassessSmryAdd == "4" | goassessSmryOdd =="4" | goassessSmryCon =="4")
```

Histogram of age by sex

```{r, echo=FALSE, message=FALSE}
ggplot(dataa,aes(x=ageInYears, fill=sex1m1)) + geom_histogram()+facet_grid(~sex1m1)
```

```{r include=FALSE}
yvar="externalizing_4factorv2"
data1 <- subset(dataa, select=c("scanid", yvar, "ageInYears", "sex1m1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
```

#Sex differences in externalizing symptoms 
Using bifactor scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1, data=data1)
summary(full.model)
```

#Interaction between age and sex on externalizing symptoms
Using bifactor scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1 + ageInYears*sex1m1, data=data1)
summary(full.model)

ggplot(data1, aes(x=ageInYears, y=yvar, fill=sex1m1, color=sex1m1)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm") 
```

#########################
```{r include=FALSE}
yvar="externalizing_corrtraitsv2"
data1 <- subset(dataa, select=c("scanid", yvar, "ageInYears", "sex1m1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
```

#Sex differences in externalizing symptoms 
Using correlated trait scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1, data=data1)
summary(full.model)
```

#Interaction between age and sex on externalizing symptoms
Using correlated trait scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1 + ageInYears*sex1m1, data=data1)
summary(full.model)

ggplot(data1, aes(x=ageInYears, y=yvar, fill=sex1m1, color=sex1m1)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm") 
```


#############

```{r include=FALSE}
yvar="nbackBehAllDprime"
data1 <- subset(dataa, select=c("scanid", yvar, "ageInYears", "sex1m1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
```

#Sex differences in overall d'
n=1154
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1, data=data1)
summary(full.model)
```

#Interaction between age and sex on overall d'
n=1154
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1 + ageInYears*sex1m1, data=data1)
summary(full.model)

ggplot(data1, aes(x=ageInYears, y=yvar, fill=sex1m1, color=sex1m1)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm") 
```












##################

#Sex differences adhd frequency
```{r include=FALSE}
data$add_bin<- ifelse(data$goassessSmryAdd ==4, 1, 0)
#data$add_bin <- as.factor(data$add_bin)
yvar="add_bin"
data1 <- subset(data, select=c("scanid", yvar, "ageInYears", "sex1m1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
```

n=1154
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1, data=data1)
summary(full.model)
```
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1 + ageInYears*sex1m1, data=data1)
summary(full.model)
 
```