---
title: "Sex_age_mfedu"
output: html_document
---


```{r include=FALSE}
library(ggplot2)
library(reshape2)
require(utils)
library(scales)
source("/home/sshanmugan/scripts/summarySE.R")
```


```{r include=FALSE}
data <- read.csv("/data/jux/BBL/projects/exec_extern_sex/inputData/data_agg/nback_n1153_from1601_20180829.csv")
data$sex01 <- as.factor(data$sex01)
```


```{r include=FALSE}
yvar="externalizing_4factorv2"
data1 <- subset(data, select=c("scanid", yvar, "ageInYears", "sex01", "medu1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
data1<- subset(data1, medu1 != "NA") #n=1138
```

#No sex x maternal education interaction on externalizing symptoms, medu -> fewer symptoms 
Using bifactor scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ sex01*medu1 + sex01 + medu1 + ageInYears, data=data1)
summary(full.model)

full.model <- lm(yvar ~  sex01 + medu1 + ageInYears, data=data1)
summary(full.model)

ggplot(data1, aes(x=medu1, y=yvar, fill=sex01, color=sex01)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm")
```

#No interaction between age x sex x medu on externalizing symptoms
Using bifactor scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01*medu1 +medu1, data=data1)
summary(full.model)

#full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01 +medu1 + medu1*sex01, data=data1)
#summary(full.model)
```



```{r include=FALSE}
yvar="externalizing_4factorv2"
data1 <- subset(data, select=c("scanid", yvar, "ageInYears", "sex01", "fedu1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
data1<- subset(data1, fedu1 != "NA") #n=1058
```

#Sex x paternal education interaction on externalizing symptoms 
Using bifactor scores. Paternal education impact on male (more edu -> fewer externalizing symptoms), but not female.
```{r echo=FALSE}
full.model <- lm(yvar ~ sex01*fedu1 + sex01 + fedu1 + ageInYears, data=data1)
summary(full.model)

ggplot(data1, aes(x=fedu1, y=yvar, fill=sex01, color=sex01)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm") 
```

```{r echo=FALSE}
#full.model <- lm(yvar ~  sex01 + fedu1 + ageInYears, data=data1)
#summary(full.model)
```

#No interaction between age x sex x fedu on externalizing symptoms
Using bifactor scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01*fedu1 +fedu1, data=data1)
summary(full.model)

full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01 + fedu1*sex01 + fedu1, data=data1)
summary(full.model)

full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01 +fedu1, data=data1)
summary(full.model)
```








```{r include=FALSE}
yvar="nbackBehAllDprime"
data1 <- subset(data, select=c("scanid", yvar, "ageInYears", "sex01", "medu1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
data1<- subset(data1, medu1 != "NA") #n=1138
```

#No sex x maternal education interaction on d', medu -> better performance
Using bifactor scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ sex01*medu1 + sex01 + medu1 + ageInYears, data=data1)
summary(full.model)

full.model <- lm(yvar ~  sex01 + medu1 + ageInYears, data=data1)
summary(full.model)

ggplot(data1, aes(x=medu1, y=yvar, fill=sex01, color=sex01)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm")

cor(data1$ageInYears, data1$medu1)
```

#No interaction between age x sex x medu on externalizing symptoms
Using bifactor scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01*medu1 +medu1, data=data1)
summary(full.model)

#full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01 +medu1 + medu1*sex01, data=data1)
#summary(full.model)
```


```{r include=FALSE}
yvar="nbackBehAllDprime"
data1 <- subset(data, select=c("scanid", yvar, "ageInYears", "sex01", "fedu1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
data1<- subset(data1, fedu1 != "NA") #n=1058
```

#No sex x paternal education interaction on d' (p=0.09) 
```{r echo=FALSE}
full.model <- lm(yvar ~ sex01*fedu1 + sex01 + fedu1 + ageInYears, data=data1)
summary(full.model)

ggplot(data1, aes(x=fedu1, y=yvar, fill=sex01, color=sex01)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm") 
```

```{r echo=FALSE}
full.model <- lm(yvar ~  sex01 + fedu1 + ageInYears, data=data1)
summary(full.model)

cor(data1$ageInYears, data1$fedu1)
```

#No interaction between age x sex x fedu on d' 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01*fedu1 +fedu1, data=data1)
summary(full.model)

full.model <- lm(yvar ~ ageInYears + sex01 + ageInYears*sex01 + fedu1*sex01 + fedu1, data=data1)
summary(full.model)

```
