---
title: "Sex Differences in Externalizing Symptoms n7053"
output:
  html_document: default
  pdf_document: default
---

```{r include=FALSE}
library(ggplot2)
library(reshape2)
require(utils)
library(scales)
source("/home/sshanmugan/scripts/summarySE.R")
```


```{r include=FALSE}
data <- read.csv("/data/jux/BBL/projects/exec_extern_sex/inputData/data_agg/n7053_from9498_20180829.csv")
data$ageInYears <- data$ageAtClinicalAssess1/12
#make sex 0/1
data$sex01 <- ifelse(data$sex==1, 0,1)
data$sex01 <- as.factor(data$sex01)
data$sex1m1 <- ifelse(data$sex==1, 1,-1)
data$sex1m1 <- as.factor(data$sex1m1)
```

Histogram of age by sex

```{r, echo=FALSE, message=FALSE}
ggplot(data,aes(x=ageInYears, fill=sex1m1)) + geom_histogram()+facet_grid(~sex1m1)
```

```{r include=FALSE}

yvar="externalizing_4factorv2"
data1 <- subset(data, select=c("bblid", yvar, "ageInYears", "sex1m1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
```

#Sex differences in externalizing symptoms using bifactor scores. n=7053
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1, data=data1)
summary(full.model)
```

bar graph of age residualized externalizing by sex
```{r echo=FALSE}
resid1<- as.data.frame(residuals(full.model, type="pearson"))
names(resid1) <- "resid"
newdata1 <- cbind(data1, resid1)
newdata2<-subset(newdata1, select=c("bblid", "sex1m1", "yvar"))
mdata <- melt(newdata1, id=c("bblid", "sex1m1"))
sdata<- summarySE(mdata, measurevar="value", groupvars="sex1m1")
ggplot(sdata, aes(x=sex1m1, y=value, fill=sex1m1)) + 
  geom_bar(position=position_dodge(), stat="identity", size = 0.8, width=0.65) +
  geom_errorbar(aes(ymin=value-se, ymax=value+se), position=position_dodge(0.65), width=0.15, size=0.8)
```


#Interaction between age and sex on externalizing symptoms using bifactor scores. n=7053
Using bifactor scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1 + ageInYears*sex1m1, data=data1)
summary(full.model)

ggplot(data1, aes(x=ageInYears, y=yvar, fill=sex1m1, color=sex1m1)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm") 
```


##########################
```{r include=FALSE}

yvar="externalizing_corrtraitsv2"
data1 <- subset(data, select=c("bblid", yvar, "ageInYears", "sex1m1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA")
```

#Sex differences in externalizing symptoms using correlated trait scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1, data=data1)
summary(full.model)
```

#Interaction between age and sex on externalizing symptoms using correlated trait scores. 
Using correlated trait scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1 + ageInYears*sex1m1, data=data1)
summary(full.model)

ggplot(data1, aes(x=ageInYears, y=yvar, fill=sex1m1, color=sex1m1)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm") 
```

#############


##########################
```{r include=FALSE}

yvar="wm_z"
data1 <- subset(data, select=c("bblid", yvar, "ageInYears", "sex1m1"))
data1["yvar"] <- data1[,2]
data1<- subset(data1, yvar != "NA") #n6825
```

#no sex differences in wm_z n=6825
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1, data=data1)
summary(full.model)
```

#no interaction between age and sex on wm_z
Using correlated trait scores. 
```{r echo=FALSE}
full.model <- lm(yvar ~ ageInYears + sex1m1 + ageInYears*sex1m1, data=data1)
summary(full.model)

ggplot(data1, aes(x=ageInYears, y=yvar, fill=sex1m1, color=sex1m1)) +
  geom_point( stat="identity", position="jitter") +
  stat_smooth(method = "lm") 
```

#############